Notes:

Add {village_enter}

Personnages:

lord: Beoson
castel: Picsalt
village: Greenhil
tavern: deadly scorpion

\section{start}

Hi, adventurer. Look how strong and inteligent you look, with the wind in your
air. I'm proud of you. You're brave. You came from far away, because you've
heared theire is a dragon in that earldom.

** présentation du monde

You should be asking yourself who I am. I'm your conscience. To be more
precisise, I'm the conscience of three adventurer: a dwarf, a man, and an elf.
Witch one are you?

Oh, I forgot to teach you that in this book, you will have to make choises. Each
time you see a number like this **number**, you can jump to that section.

Let's get back to the topic in hand, you will have tree attempt to succed you
mission, one as a dwarf \ref{dwarf}, one as an elf \ref{elf}, and one as a
\ref{human}. Choose wise, and be successfull. If not, you can try again as
another adventurer.

\section{human}

As a human, you have a general knowledge of the local region. People can help
you, but will still consider you as a stranger.

Sometime, you are supertitious, and you know that going into the darkest place
of a forest can be a bad idea.

You are mercenary. The local lord, Beoson appointed you as a dragon killer. You
will not fail in you task, and you are well trained. When this task will be
completed, you will have to see him back to claim your bounty.

As soon as the appointment was taken, and after shaking you hand a sign of trust
with Beoson, you go back to the courtyard of this castel \ref{courtyard}.

\section{dwarf}

... you own a dwarf axe of first quality ...

\section{courtyard}

The inside of the castel of Picsalt is ...

You can acces to the apartment of the lord only if you have a proof that you
killed the dragon \ref{lord}.

If this is not the case, then go search it! You can take your time in the local
contryside \ref{field} or walk in one go directly to Greenhil, the nearing
village \ref{village}.

\section{lost}

The wood seems darker and darker. You have the impression to be stared by a
malicious presence. 

...

At a point you are sur that you are lost. You are sure that you are lost. I
cannot help you. To be honnest, I will not even remember you. It's the end.

Maybe you will be more careful as a human \ref{human}, a dwarf \ref{dwarf} or an
elf \ref{elf}.

\section{village}

You are enterring into Greenhil, a small village. Somme kids are playing into
the mud. The roof of the thatched cottage are not in their prime youth.
Nevertheless, the inhabitant don't seem to starve.

You gaze around you, looking for some shop. After all, you found a smithy
\ref{blacksmith}, and a tavern \ref{tavern}. During your research, a little girl
got your attention \ref{children}.

\section{blacksmith}

You come near the forge. The blacksmith is working, hurting a piece of iron with
is hamer, probably creating a sword.

If your are a dwarf, shout out him in \ref{blacksmith_dwarf}, otherwise look is
work on \ref{blacksmith_nothing}.

\section{children}

Unlike what you were expected, the children are talkative. Even if their speech
are a bit rambling, you get the main idea. Near the forest, a huge monster
(probably your dragon) was seen. A child added, that it's not a good idea to go
to the darkest place in the forest.

After that break, you can go to the blacksmith \blacksmith or take a drink in
the tavern \tavern.

\section{blacksmith_dwarf}

The dwarf are the best blacksmiths in that world. You look amused by the
simplicity of his work. If you really need a sword of bad quality, by it in
\ref{blacksmith_sword}, otherwise go back into the village (\ref{village})

\section{blacksmith_sword}

Holding back your shame of buying a weapon of such a bad quality, you pay the
blacksmith. Now you have a \textbf{sword}. At leat you are able to defend
yourself if needed.

Go back to the village \ref{village}.

\section{tavern}

You enter into the tavern. It is called \textit{Deadly scorpion}, even if the
alcool look as dangerous as fresh water! At least, the air is hot, and the
peoples look hostpitable.

You can drink alone in \ref{tavern_drink}, or you can install yourself with the
the others customer and listen rumours (\ref{rumour}).

\section{tavern_drink}

The wine looks so rough and the beer smells so hard that you have preffer to
take a cup of mead. Their is so few thing to do in that place, that you take a
second one, and a third, … to the point that the sun start falling.

You choose to stay in that place to sleep. The baterder give you a place in the
straw, with a cow in exchange of some coin. It's not fair, but you are too drunk
to protest.

You sleep in one go in \ref{village_morning}.

\section{rumour}

The inhabitant of Greenhil are simple farmers, but they know their realm in
details. After speaking of the sun, the influence of the moon on their beans and
on the tax, they finnally give a usefull information. The lumberjack saw
recently some scarry track.

Glanning all those hearsay took you the whole day. The deadly scorpion is also a
place where so can eat and sleep, so you choose to stay there for the night.

The inkeeper serve you some meat with beam of the last year. It is not
excellant, but at least your stomach is full!

After that, you go to sleep in a small bedroom with a bed of straw, in
\ref{village_morning}.

\section{village_morning}

You have take a good night. The cockerel wake you with the first sunbeams. You
stand up, some straws still in your hair.

You decide to start your day as fast as possible, and to leave that village.
You can go into the field of weat \ref{field}, the main road \ref{road}, or
going to the edge of the nearest forest \ref{lumberjack}. %%% -> rewrite

