\section{castle_entrance}

You stand front the closed gate of the castle. A guard shouts out:

-- Hey stranger, what are you doing here?

If you are a human, you can respond that you are currently in a mission for Lord
Beoson, and the watchman will open the gate for you~($\diamond$~\ref{courtyard}~$\diamond$).

Otherwise, the sentry will ignore you without restraint. The only choice
left to you is going back to the country~(\ref{field}).

\section{courtyard}

The courtyard of the castle of Picsalt is muddy, like many strongholds. You do
not make yourself late for such a detail. If you have a proof that you have
killed a dragon, then you will be allowed to access to the apartments of the
lord~($\diamond$~\ref{lord}~$\diamond$).

Otherwise, go back to your quest outside of this castle. They is no dragon
there! You can take your time in the local countryside~(\ref{field}) or walk in
one go directly to Greenhil, the nearest village~(\ref{village}).

\section{lord}

With a warm welcome, lord Beoson asks you a proof of your exploit.  You open
your purse and clear it out of its contents on a table. Beoson comes close,
intrigued. You get out of your stuff the two eyes of the dragon.

-- Nice job, said the lord.

Only with a short glance, he gives some order to his chamberlain. Some time
later, the domestic comes back with a small chest: the five thousand coins of
your reward!

\medbreak

Congratulation, you have accomplished your mission. Do you want to try again as a
Dwarf~(\ref{dwarf}) or as an elf~(\ref{elf})?
