\section{chapel}

You enter in the small chapel. The architecture is gothic. There is not so much
light inside, even if small stained windows try to bring rays on a statue.

You sit on a bench and set yourself for a private prayer.

A churchman seems to be busy on a manuscript. You can either engage him in
conversation~(\ref{priest}), or enter inside the nearest
forest~(\ref{edge_of_the_wood}). Some mighty creature might live in that place.

\section{priest}

The old man is concentrated on his work. You salute him in your native language.
If you are an elf, he answers you in~($\diamond$~\ref{priest_elf}~$\diamond$).

Otherwise, he blesses you quickly and continues his work. In that case, you feel
sorry to have disturbed him. You decide either to enter the
forest~(\ref{edge_of_the_wood}) or to get back the main road~(\ref{road}).

\section{priest_elf}

The ecclesiastic raises his head in your direction.

-- It's been a long period since the last time I've seen an elf. What are you
doing here?

At the beginning of that story, you brought a flask with you. If it is still
empty, continue your discussion in~($\diamond$~\ref{priest_quest}~$\diamond$).

Otherwise, pull it
out~(\ref{theology}).

\section{priest_quest}

You explain that you heard the rumour that maybe a dragon may leave in that
country. Therefore, you came to study it.

The old man looks at you, and adds:

-- You should go into the forest. Some rumours say that dragon's tracks have
been seen there. That forest is dangerous, but since you are an elf, it will not
be a problem to get your bearings. Come back here when you have found and
studied the creature.

You thank him and assure that you will return. You leave the chapel, and enter
to forest~(\ref{edge_of_the_wood}).

\section{theology}

While you are showing the dragon's tears inside your flask to the churchman, you
analyse the observations you made on the dragon. The old man seems fascinated by
the reflects of the iridescent light that arises from the liquid.

He leads you in his library. He pulls a book and starts to teach you the advanced
magical properties of dragons' tears. That discussion is simply engaging.
Once you have finished, you thank him warmly for having transmitted his
knowledge.

Congratulation, you quest is ended. Now you are free to continue a new
adventure. Maybe you can try as a human~(\ref{human}), or as a
dwarf~(\ref{dwarf}).
