
\section{field}

The road snake between some small fields. The weather is cloudy and sad, but
your are full of energy.

You take a break to admine the panorama. Some sunbeams witch cross clouds
illiminate some farmers. The ploughmans are leaning on their swing plow,
probably chatting about the constantly changing weather.

The landscape is feeric with a vast forest filled of mist in the
background~(\ref{edge_of_the_wood}). In its border, there is a small chapel made
of stone~(\ref{chapel}). In the opposite direction, an old castel overlook the
vale~(\ref{castel_entrance}).

You notice the smoke of some house behind a hill. That should be a village. You
are pretty sure that you can found some information over there~(\ref{village}).

\section{road}

You walk during approximatively a mile before reaching a marker sign. If you are
an adventurer with a gold treasure, you can continue your journey far from there and
the dragon~(\ref{gobelins}).

Otherwise, the village of Greenhil is indicated on the west~(\ref{village}), and
the road continue in direction of the Picsalt castel~(\ref{field}). A last
choise is offer only for dwarfs: follow a small beaten path~(\ref{track}).

\section{gobelins}

You are a rich dwarf! Thoses words nicely in your head. You walk with a cheerful
pace, your mind a bit elsewhere when suddendly some gobelins jumps all around
you!

I hope you have taken the time to find a new weapon after defeting the dragon. If
you were wise, pull it out in~(\ref{dwarf_victory}). If not, … do what you can
in~(\ref{dwarf_death}).

\section{treasure}

Your sharpened eyes get an imperceptile flash. It is the reflection of a gold
nugget. All dwarfs know that any dragon, even the youngest keep a treasure. That
was your main motivation when you come here. You stole your reward, and hide it
in your bag. At least that will easily cover the cost of a skilful blacksmith
for your axe.

Get the road back on~(\ref{road}).

\section{dwarf_victory}

The small creature underestimated you. With a nimble gesture, you took your new
sword. You defeat them, some dragon fire in your eyes. The battle is epic, but
quite short. Your aggressor run away, far from your revange.

You salvage what you can found on their warm corpses. Then, in one gesture you
clean your weapon and put it away. It's a good sword, of lower quality than your
broken axe, but good enough to suit your need. Your continue your journey,
confident in your future. Congratulation!

Do you think you will have such a great adventure as a human~(\ref{human}) or
an elf~(\ref{elf})?

\section{dwarf_death}

Dear god of dwarf, your axe is broken! Without having the time to improvise
anything, your opponents jump on you. Their tiny claws impale your body. Your
death is so shameful, that you are not sure that will be able to resurect as a
human~(\ref{human}), not even as an elf~(\ref{elf}).
