\section{track}

While you walk along some trees, you found some gigantic tracks. Without a
shadow of a doubt, you identify them as dragon's. You follow them, with
the goal to find it.

The tracking is in fact quite simple. That beast seems to have neither fear, nor
need to hide. You follow the marks during a quarter of a mile. They continue in
the grassland. At the turning of a rock, you finally found the mighty creature.
It seems to be asleep, curled up on itself.

Are you in a bloody mood, and do you want to kill that mythical creature while it
is defenceless~(\ref{dragon_battle}), or do you prefer to study its
habits~(\ref{dragon_studied})?

\section{dragon_battle}

If you are an elf, your battle will continue in~(\ref{battle_death}).

\medbreak

Otherwise, you softly pull out you weapon from it cover. You carefully take a
step closer, and with a sharp movement you notch the neck of the dragon. It wakes
up instantaneously and try to burn you! You avoid the flames with a side jump.
Even if a short but brutal battle begin, your knock proves to be lethal. The
beast try to avenge it future death without success.

Finally, the mighty creature pass away. You extract both of its eyes as a
trophy. If you are a dwarf, you also found something in~(\ref{treasure}).
Otherwise, go to the village to celebrate your
victory~(\ref{human_drink_victory})!

\section{dragon_studied}

You move closer to the dragon. Lots of bones lie around it. If you are not an
elf, you accidentally broke one and the sound will wake it
up~(\ref{battle_death}).

\medbreak

Otherwise, you are careful enough to let the creature sleep. That deadly living
being is splendid. Purples and green reflections waves on its scales. It breath
slowly. You notice that the dragon seems to cry. You take a flask from your belt
and carefully salvage a tear.

One you have finished your studies, you go back to the main road. You can either
move to the closest village~(\ref{village}), or continue to some new adventure
far away in the est~(\ref{elf_road}).

\section{treasure}

Your sharpened eyes get an imperceptible flash. It is the reflection of a gold
nugget. All dwarfs know that any dragon, even the youngest keep a treasure. That
was your main motivation when you come here. You stole your reward, and hide it
in your bag.

Unfortunately, your axe was broken during the battle. It cannot be used anymore.
At least that treasure will easily cover the cost of a skillful blacksmith.

Get the road back on~(\ref{road}).


\section{elf_road}

Oh! Did you forget to visit the old mystic of that region before going
elsewhere? I told you that you had to do it in the introduction. It is so
shameful that you can start again with an inferior race: as human~(\ref{human})
or dwarf (\ref{dwarf})!

\section{battle_death}

The mighty creature notices you irritated. With some fire in its eyes, it burns
you in one breath. You were not prepared for a death battle. Without having the
time to defend yourself, your flesh is chopped by the deadly dragon's claws.

\medbreak

In a minute, your timeless journey begin in the afterword. Do you want to resurrect
as a human~(\ref{human}), a dwarf~(\ref{dwarf}) or as an elf~(\ref{elf})?
