\section{road}

You walk during approximatively a mile before reaching a marker sign. If you are
an adventurer with a gold treasure, you can continue your journey far from there and
the dragon~(\ref{gobelins}).

Otherwise, the village of Greenhil is indicated on the west~(\ref{village}), and
the road continue in direction of the Picsalt castel~(\ref{field}). A last
choise is offer only for dwarfs: follow a small beaten path~(\ref{track}).

\section{track}

While you walk along some trees, you found some gigantics tracks. Without a
shadow of a doubt, you identify them as dargon's. You follow them, with
the goal to find it.

The tracking is in fact quite simple. That creature seems to have no fear, and
seems to have no need to hide. You follow them during a quarter of a mile. The
tracks continue in the grassland. At the turning of the rock, you finally found
the mighty creature. It seems to be aspleep, curled up on itself.

Are you in a bloody mood, and do you want to kill that mythical creature while it
is defensless~(\ref{dragon_battle}), or do you prefer to studie its
habits~(\ref{dragon_studie})?

\section{dragon_battle}

If you are a elf, your battle will continue in~(\ref{battle_death}).

--------------


You extract the two eyes of the dragon, as a trophy. If you are a dwarf, you
also found something in~(\ref{treasure}). Otherwise, go to the village to
celebrate your victory~(\ref{village})!

\section{dragon_studie}

You move closer to the dragon. Lots of bones lie around it. If you are not an
elf, you accidentally broke one. The sound wake up the creature that attack you
in~(\ref{battle_death}).

Otherwise, you are careful enough to let the creature sleep.

---------
The dragon seems to cry. You take a flask from your belt and carefully salvage a
tear.

One you have finished your studie, you go back to the main road. You can either
goin back to the village~(\ref{village}), or continue to some new adventure far
away in the est~(\ref{elf_road}).

\section{elf_road}

Oh! Did you forget to visit the old mistic of the region before going elsewhere.
It told you that you had to do it in the introduction! It is so shameful that
you can start again with an inferior race: as human~(\ref{human}) or as a dwarf
(\ref{dwarf}).

\section{gobelins}

You are a rich dwarf! Thoses words nicely in your head. You walk with a cheerful
pace, your mind a bit elsewhere when suddendly some gobelins jumps all around
you!

I hope you have took the time to find a new weapon after defeting the dragon. If
you were wise, pull it out in~(\ref{dwarf_victory}). If not … do what you can
in~(\ref{dwarf_death}).

\section{treasure}

Your sharpened eyes get an imperceptile flash. It is the reflect of a gold
nugget. All dwarfs know that any dragon, even the youngest keep a treasure. That
was your main motivation when you come here. You stole your reward, and hide it
in your bag. At least that will easily cover the cost of a skilful blacksmith
for your axe.

Get the road back on~(\ref{road}).

\section{dwarf_victory}

The small creature underestimated you. With a nimble gesture, you took your new
sword. You defeats them, some dragon fire in your eyes. The battle is epic, but
quite short. Your aggressor run away, far from your revange.

You salvage what you can found on their warm corpses. Then, in one gesture you
clean your weapon and put it away. It's a good sword, of lower quality than your
broken axe, but good enough to suit your need. Your continue your journey,
confident in your future. Congratulation!

Do you think you will have such a great adventure as a human~(\ref{human}) or
an elf~(\ref{elf})?

\section{dwarf_death}

Dear god of dwarf, your axe is broken! Without having the time to improvise
anything, your opponents jump on you. Their tiny claws impale your body. Your
death is so shameful, that you are not sure that will be able to resurect as a
human~(\ref{human}), not even as an elf~(\ref{elf}).

\section{battle_death}

The mighty creature notice you irritated. With some fire in its eyes, it burn
you in one breath. You were not prepared for a death battle. Without having the
time to defend youself, your flesh is choped by the deadly claw of the dragon.

\medbreak

In a minute, your timeless journey begin in the afterword. Do you think it will
be better as a human~(\ref{human}), a dwarf~(\ref{dwarf}) or as an elf~(\ref{elf})?
