\section{lost}

The wood seems darker and darker. You are under the impression to be stared at a
malicious presence. The light decreases progressively. You finally decide to
sleep there, since you will not able to find the exit of that forest before the
night.

Your night is awful. Each time you are starting to fall asleep, something wakes
you up with a start. As soon as the aurora raises you continue to walk, hoping
to escape of that place. At a point you are convinced that you are lost. I
cannot help you. To be honest, I will not even remember you. It's the end!

\medbreak

Maybe you will be more careful in your next incarnation as a
human~(\ref{human}), a dwarf~(\ref{dwarf}) or an elf~(\ref{elf}).

\section{edge_of_the_wood}

You stand at the edge of the wood. If you are a dwarf, progress immediately
on~($\diamond$~\ref{dwarf_edge_of_the_wood}~$\diamond$).

\medbreak

Otherwise, you walk between trees and bushes. You have a strange impression.
That forest seems to have its own personality. At a point, you notice that you
cannot see anything but trees… except that clearing~(\ref{clearing_1}).

\section{dwarf_edge_of_the_wood}

Your grandmother did not repeat you enough time that going into the woods is
the worst thing you could ever do? All forests are evil, they all full of trees!
You have the immediate feeling that it was a really bad idea to came here.

You roam under the terrifying oaks, and the malicious pine trees~(\ref{lost}).

\section{clearing_1}

You feel that it is a good time to take a nap and eat a bit. After that
break, you are in better shape. You look all around you. The only thing that can
be seen is trees.

You can guess the far-off the sound of a river~(\ref{river}). In the opposite
direction, the lobed-leaved trees seem older, as if they were darker but more
majestic~(\ref{old_tree}).

\section{clearing_2}

You get into a clearing with the feeling of going in circles in that forest.
Only an elf will notice the small differences between all those trees and keep a
sane mind~(\ref{natural_basin}).

Otherwise, you have no idea where you are in that disturbing forest. You walk
with less and less hope of going out of this place one day~(\ref{lost}).

\section{lumberjack}

You progress between trees, following some sort of path. Your steps will carry
you in front of a small house. A man is cutting wood with his axe. He notices
and greets you.

You take time to discuss and share some food with him. The guy is nice, and when
you have finished explaining that your are trying to find dragon, he explains
you where he saw some gigantic tracks for the last time.

He can lead you to the tracks~(\ref{lumberjack_2}), but maybe you prefer to pry
first in a nearby chapel~(\ref{chapel}), or continue alone~(\ref{edge_of_the_wood})

\section{natural_basin}

Your sharpened eyes saw a small light reflecting on leaves. It must come from some
liquid. You walk in its direction and found a pond of vision. It's a perfect
circle of white stone that contains pure water. You lean closer, and suddenly the
reflections turn cloudy. An image appears at the surface of the fluid. Even if it
is not clear, you have the feeling that it's a map of the region. At the west of
a village, in the country, you see an old site of prayer. But what catches your
attention is something to the est, near you.

The vision fades out progressively. You take a short nap, and eat a bit
since magic is tiring. Then, find your way with a decided step in~(\ref{track}).

\section{river}

You follow a tiny river which snakes between trees during a long time. You found
the atmosphere oppressive, full of humidity. Far away, you ear a damp sound.
It's repetitive. Something like ``\textit{Tchack… tchack… tchack…}''. You can
get a step closer~(\ref{lumberjack}), or in the opposite
direction~(\ref{clearing_2}).

\section{old_tree}

You have a strange impression. The trees that surround you are not only old, but
it is like they have some sort of consciousness. You do not feel in your proper
place.

Hopefully, you quickly found another clearing~(\ref{clearing_2}). You feel a bit
better after leaving that area.

\section{lumberjack_2}

The lumberjack guides you during half of the distance. He says it is too dangerous
now for him to continue, but he describes with precision where he thinks that you
will find the mighty creature. After that, he returns to his work.

If you are a dwarf your progression with bring you
on~($\diamond$~\ref{dwarf_edge_of_the_wood}~$\diamond$), if not you will arrive
in~(\ref{track}).
