\section{start}

The world is vast, but that adventure will take place in
the contry of Greenhil. You came here where you heard that a dragon settle in
that area. Lord Beosn, protector of that earldom live in the nearest castel:
Picsalt. Even if there are only humans who lives in the region, it is not
uncommon to see dwarfs, elfes, or even magicals creatures.

Oh, I forgot to teach you that in this book, you will have to make choises. Each
time you see a number like this~(\ref{start}), you can jump to that section.
Sometimes it is a mandadory choise.

Let's get back to the topic in hand, you will have tree attempt to succed you
mission, one as a dwarf~(\ref{dwarf}), one as an elf~(\ref{elf}), and one as a
(\ref{human}). Choose wise, and be successfull.

\section{xx}

Oh! What are you doing? You cannot go to that paragraph. Go back to
(\ref{start}) little cheater!

\section{human}

As a human, you have a general knowledge of the local region. People can help
you, but will still consider you as a stranger. You are a mercenary. The local
lord, Beoson appointed you as a dragon killer. When your task will be completed,
you will have to let him see a trophy to claim your bounty.

You are a bit supertitious, and you know that going into the darkest place
of a forest can be a bad idea, at leat without a guide.

As soon as the appointment was taken, and after shaking you hand a sign of trust
with Beoson, you go back to the courtyard of this castel~(\ref{courtyard}).

\section{dwarf}

You are a proud representative of dwarfs warrior, with your axe of first
quality. You came into that region because you know that all the dragons hold a
treasure. It is maybe your chance to become rich and influent in your own
underground kingdom.

When you were young, your granny always repeated you that forests are the
dangerous places in that world. You remember that the warm coming from the
stone's fireplace, and her soft voice in her beard was so contrasting with her
warning. They are no way to go in those place, even with a guide.

But nowadays, you are an adventurer. The weather is cloudy, and the air is
fresh. Your story begin in the country~(\ref{field}).

\section{elf}

When you heard that a dragon come to the country of Greenhil, you though it was
time to make something of your life. You are young, only two or three hundreds
of spring. Your objective is to study that mighty creature. When you will have
completed that first quest, you will also have to meet an old priest that live
somewhere in the country before leaving the region.

Your adventure begins in the best place that you can encounter: the edge of a
wood~(\ref{edge_of_the_wood})!
