% TODO
% Add {village_enter}

\section{village}

You are in Greenhil, a small hamlet. Some kids are playing into the mud. Even
if the roofs of the thatched cottages are not in their prime youth, the
inhabitants don't seem to starve.

You gaze around you, looking for some shop. You found a
smithy~(\ref{blacksmith}), and a tavern (\ref{tavern}). During your research, a
little girl got your attention~(\ref{children}).

\section{blacksmith}

You come to the forge. The blacksmith is working, hitting a piece of iron with
his hammer. He is probably creating a sword.

If your are a dwarf, shout out to him in~(\ref{blacksmith_dwarf}), otherwise
look at his work on~(\ref{blacksmith_nothing}).

\section{children}

Unlike what you were expecting, the children are talkative. Even if their speech
are a bit muddled, you get the main idea. Near the forest, a huge monster
(probably your dragon) was seen. A child added, that it's not a good idea to go
to the darkest areas of forests.

After that break, you can go to the blacksmith~(\ref{blacksmith}) or take a drink in
the tavern~(\ref{tavern}).

\section{blacksmith_dwarf}

In your opinion, dwarves are the best blacksmiths in that world. You look amused
by the simplicity of his work. If you really need a new weapon, you can
purchase a sword.

You decide to take a drink at the tavern~(\ref{tavern}).

\section{blacksmith_nothing}

You watch with attention the craftsman's work. The way he models the steel is
fascinating. You exchange some banalities. Since you have no need for the fruit
of his labour, you will go back to the main place of the village~(\ref{village}).

\section{tavern}

You enter into the alehouse. It is called \textit{Deadly scorpion}, even if
alcohols look as dangerous as fresh water! At least, the air is hot, and people
seem hospitable.

You can drink alone~(\ref{tavern_drink}), or install yourself with others
customers to listen to rumours~(\ref{rumour}).

\section{human_drink_victory}

You are proud of your victory! You walk to Greenhil with a cheerful pace. Once
you arrive in the village, you find your way to the tavern~(\ref{tavern_drink}).

\section{tavern_drink}

The wine looks so rough and the beer smells so hard that you have preferred to
take a cup of mead. There is so little to do in that place, that you take a
second one, and a third, … to the point you start falling.

You choose to stay in that establishment to sleep. The bartender gives you a place in the
straw with a cow, in exchange of some coins. It's not fair, but you are too drunk
to protest.

You sleep in one go until~(\ref{village_morning}).

\section{rumour}

The inhabitant of Greenhil are simple farmers, but they know their realm in
details. After speaking of the sun, the influence of the moon on their beans and
taxes, they finally give a useful piece of information. The lumberjack saw
recently some scary tracks.

Gleaning all this hearsay took you the whole afternoon. The \textit{Deadly
scorpion} is also a place where you can eat and sleep, so you choose to stay
there for the night.

The innkeeper serves you some meat with beams of the last year. It is not
excellent, but at least your stomach is full! After that, you go to sleep in a
small bedroom with a straw mattress~(\ref{village_morning}).

\section{village_morning}

It was a good night. The cockerel wakes you with the first sunbeams. You stand
up, some wisps still in your hair.

You decide to start your day as fast as possible, and to leave that village.
You can go to the west into the open lands~(\ref{field}), the main
road~(\ref{road}), or to the edge of the nearest forest~(\ref{lumberjack}).

