\section{field}

The road snake between some small fields. The weather is cloudy and sad, but
your are full of energy. You notice the smoke of some house behind a hill. That
should be a village. You are pretty shure that you can found some information
over there~(\ref{village}).

You notice a vast forest, filled of mist~(\ref{edge_of_the_wood}). In its
border, their is a small chapel made of stone~(\ref{chapel}).

Finnaly, you catch sight of farmers working in their fields~(\ref{farmers}).

\section{field_2}

You take a break to admine the landscape. Some sunbeam witch cross clouds
illiminate some farmers~(\ref{farmers}) next to a small chapel (\ref{chapel}).
The landscape is a bit feeric with a vast forest in the background. In the
opposite direction, an old castel overlook the vale~(\ref{castel_entrance}).

\section{farmers}

You great the to ploughman. They was leaning on their swing plow, chatting about
the constantly changing weather.

After a shord discussion, in witch you explain that you are an adventurer, they
take some time to explain you the local geographie. If you want to go to into
the forest, you should first visit the lumberjack~(\ref{lumberjack}). Also, it
cannot be a bad idea to go to see lord Beoson in his castle
(\ref{castel_entrance}), or visit the tavern of the village~(\ref{village}).

You thanks the workers and continue your way.

\section{chapel}

You enter in the small chapel. The architecture is gothic. Their is not so much
light inside, even if the small stained glasses try to bring some sunbeam on a
statue.

You sit on a bench and engage yourself in a private prayer.

When you have finished, you wall back out into the fresh air. Now, you can
either talk to the priest~(\ref{priest}), witch seems to be busy on a
manuscript, or enter into the nearest forest~(\ref{edge_of_the_wood}). It can be
possible that some mighty creature leave in that place.

\section{priest}

The old man is concentrate in his work. You salute him in you native language.
If you are an elf, he reply you in \ref{priest_elf}. Otherwise, he bless you
quickly and continue his work. In that case, you feel sorry to have disturbate
him, and decide to enter into the forest~(\ref{edge_of_the_wood}).

\section{priest_elf}

The ecclesiatic raise is head in your direction.

-- It's been a long period since the last time I've seen an elf. What are you
doing here?

You explain to the church's man that you heared the rumour that maybe a dragon
may leave in that country, and you came to study it.

At the beggining of that story, you bring a flask with you. If it is still
empty, continue your discussion in \ref{priest_quest}. Otherwise, pull it out,
and show it in \ref{theologie}.

\section{priest_quest}

The old man look at you, and adds:

-- You should go into the forest. Some dragons' tracks have been found in that
place. That forest is dangerous, but since you are an elf, it will not be a
problem to locate yourself. When you will found and study it, come back here.

You thanks him and assure that will come back. You go out of the chapel, and
enter into to forest~(\ref{edge_of_the_wood}).

\section{theologie}

You show the church man the dragon's tears inside your flask. The old man seems
facinated by the reflects of the iridescent light that arise from the liquid.

He leads you in his library. He pull a book and start to teach you the advanced
magical properties of the dragon's tears. That discussion is simply
pationnating. When you have finnished, you thanks him warmfully to pass on his
knowledge.

Congratulation, you quest is ended. Now you are free to continue a new
(adventure. Maybe you can try as a human~(\ref{human}), or as a dwarf
(\ref{dwarf}).
